The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-07-12 paper/paper.tex
Updating

@@

sensitively on the progenitor's metallicity, to the extent that rare low-metallicity star formation during galaxy

@@

factors of order  unity, and even binary neutron star populations differ by tens of percent.  \jillianremark{add sentence about mass dependence (more in dwarfs).}

@@

@@

%Add me: \cite{Kirby13}
\editremark{Jillian}: Add me but note conflict \cite{Somerville15}, etc or \cite{2015ARAA..53...51S}

@@

\section{Introduction}
% POINT: LIGO soon will detect compact binary mergers....
%     ... and possibly EM counter part too
%     ... which will enable new physics
Gravitational waves have been detected from  coalescing  black hole binaries \citep{DetectionPaper,LIGO-O1-BBH}. 
Over the next few years, ground-based gravitational wave detectors like LIGO 
and Virgo  should detect the gravitational
wave signal from many more similar merging compact binaries \citep{LIGO-O1-BBH,RatesPaper,gwastro-EventPopsynPaper-2016}, as well as  binary  neutron stars and black hole-neutron star binaries \citep{LIGO-Inspiral-Rates,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
%
The host galaxies of gravitational wave sources will be identified, either directly or statistically.  
On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
% People we can't afford the space to cite, alas:
%    - 2015arXiv150101986H   -
%    - 2013MNRAS.430.2121P - Rosswog recent
%    - Shibata group/Koutarou
In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
the sky position and therefore approximate birthplace of each merging binary.    
%
On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \citep{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
networks increase in number and sensitivity, these localizations will allow statistical and, eventually, unique identification of
host galaxies directly, even without associated electromagnetic emission.
%
As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
formation; see, for comparison,  \citet{2011MNRAS.412.1508M}, \citet{long-grb-GuettaPiran2007},
\citet{2014ARAA..52...43B}, and references therein. %2010ApJ...722.1879M,2010MNRAS.407.1314M}.     
%

@@

%{\bf Richard go ahead and edit this however is needed.}  
The evolution
of a galaxy, in terms of its stellar mass and metallicity evolution,
depends strongly on its interaction history.  Galaxies which appear
similar at the present day may have had drastically different
histories, which may result in differences in compact object merger
rates.  To investigate whether galaxy history affects the GRB event
rate, we have chosen two simulations which are extremely similar at $z
= 0$ but differ strongly in their merger histories; see Figure \ref{fig:images}.

@@

  Due to the differences in merger histories, the star formation histories and metallicity
  evolution of h258 and h277 also differ at early times.  Figure
  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of the two galaxies.  The star formation histories are quite different at early times, where h277 has larger bursts of star formation between 2-4 Gyr, but h258 has a large burst at $\sim 6$ Gyr during a major merger.   The right panel shows the mean metallicity of
  recently formed stars vs time (thick solid lines), where we define
  recent as within the past 50 Myr.  The shaded regions correspond to
  one standard deviation of the mean, while the thick dashed lines
  represent the top and bottom 90\%.  We see that the early evolution
  of the metal properties of these galaxies does differ - between 0.5
  and 6 Gyr, h277 hosts a \emph{modestly}  more metal-rich population than
  h258.   For most astrophysical processes, the small metallicity difference illustrated here will have no impact on
  present-day observables.  However, for binary black holes depend sensitively on all low metallicity star formation
  over cosmic time; as we show below, these small differences can have an observable impact at present.

@@

Our goal in this work is to estimate the \emph{ratio} of compact binaries that should be merging, at present, in the two
simulated galaxies described above.

To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; \jillianremark{this is first mention of PSG and PSE, define} similar approaches have been used by
\cite{2016arXiv160508783L} and others.

@@

\begin{widetext}
% POINT:  Model
To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
\begin{eqnarray}
V = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 dm_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
\end{eqnarray}
where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron
stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum 
black hole mass $M_{max}(Z)$ allowed by
\emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
  therein]{gwastro-EventPopsynPaper-2016}.  In agreement with much more detailed prior work \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, this simplified model yields typical chirp masses for BH-NS binaries that
vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume  comparable-mass binaries
form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
 between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise, adopting a fiducial exponent $p=2$; see, e.g.,
\cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
detection-weighted mass distribution [$\propto p(m_1,m_2)
\mc^{15/6}$] depends weakly on mass [$ p(m_1,m_2)
\mc^{15/6} \propto m_1^{-0.5} \delta(m_1-m_2)$.  In our simple model, the total  and chirp mass
distributions   are qualitatively consistent with detailed  binary evolution calculations \citep{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.

@@

% POINT: 
To characterize how often compact binaries form and coalesce, we use the ansatz adopted in \abbrvPSellipticals{} and
\abbrvPSgrb{}: for a star-forming parcel of mass $\Delta M$ the number of binaries born at time $0$ which
are coalescing now is $\lambda \Delta M dP/dt$, where $\lambda$ is an overall efficiency per unit mass and $P(<t|Z)$ is
a metallicity-dependent delay time distribution.\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
    In this paper we are investigating the relative contribution of
different star-forming environments and galaxy evolutionary histories, not the overall normalization, so the overall scale of $\lambda$ is irrelevant.  
However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact
objects, we adopt a power law
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{min}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adopt a  concrete scale
factor  $
\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
%
For binaries containing neutron stars, for simplicity and without loss of generality we adopt the universal delay time distribution
%% Finally, we parameterize the delay time distribution by  either
%% \begin{eqnarray}
%% P_t(<t) &=& \begin{cases}
%% 0 & t<10 \unit{Myr} \\
%% (t/13\unit{Gyr})^{b}& t \in [10\unit{Myr},t_H]
%% \end{cases} 
%% \end{eqnarray}
%% with $b> 0$ or as the special case
\begin{eqnarray}
\frac{dP_t(<t)}{dt} =  \begin{cases}
0 & t<10 \unit{Myr} \\
\frac{1}{t \ln (13 \unit{Gyr}/10\unit{Myr})} & t \in [10\unit{Myr},13\unit{Gyr}]
\end{cases} 
\end{eqnarray}
\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
  These variations have less impact on our results than the evolving metallicity distribution of star forming gas.}
%
For binary black holes forming at metallicities $Z<0.25 Z_\odot$, we adopt the same prescription.  To be qualitatively consistent
with detailed binary evolution calculations at near-solar metallicity (e.g., \abbrvPSellipticals{} and
\cite{gwastro-EventPopsynPaper-2016}), for 
black holes forming at metallicities $Z>0.25 Z_\odot$ we adopt a much more uniform delay time distribution, so 
coalescing black hole binaries have nearly uniform delay time distribution between $100\unit{Myr}$ and
$13\unit{Gyr}$\editremark{checkme again - a little hacky}; that said,  our conclusions are not sensitive to this choice.
%
For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
evolution  \citep{2010ApJ...715L.138B,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2-StarTrackRevised-2012}.

For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
  an extreme example of this well-known trend.]  In practice, however, binary black holes produced near solar
metallicity correspond to a relatively small proportion of the overall population; we therefore neglect this
effect\footnote{may want to change}.

% POINT: Net effect
Therefore, up to an irrelevant overall scale factor, the  present-day detection-weighted coalescence rate $r_D$  of binary compact objects formed by within two similar
galaxies  can be calculated via
\begin{eqnarray}
 r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP}{dt}(t) \dot{M} p(\log Z|t)
\end{eqnarray}

@@

\begin{table}
\begin{centering}
\begin{tabular}{|ll|l|}\hline
 \text{\BoringGalaxy} & \text{BHBH} & 0.0996 \\
 \text{\ExcitingGalaxy} & \text{BHBH} & 0.0912 \\
 \text{\DwarfOne} & \text{BHBH} & 0.212 \\
 \text{\DwarfTwo} & \text{BHBH} & 0.76 \\
 \text{\BoringGalaxy} & \text{BHNS} & 0.000219 \\
 \text{\ExcitingGalaxy} & \text{BHNS} & 0.000264 \\
 \text{\DwarfOne} & \text{BHNS} & 0.000275 \\
 \text{\DwarfTwo} & \text{BHNS} & 0.000235 \\
 \text{\BoringGalaxy} & \text{NSNS} & 0.0000592 \\
 \text{\ExcitingGalaxy} & \text{NSNS} & 0.0000715 \\
\hline
\end{tabular}
\end{centering}
\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
  discussed.  
}
\end{table}

>>>>

%<<<<<<< Updated upstream

@@

sensitively on the progenitor's metallicity.  Rare low-metallicity star formation during galaxy

@@

factors of order  unity, and even binary neutron star populations differ by tens of percent.  
We also demonstrate by concrete example the extent to which dwarf galaxies overabundantly produce compact binary
mergers, particularly binary black holes. 

@@

%\editremark{Jillian}: Add me but note conflict \cite{Somerville15}, etc or \cite{2015ARAA..53...51S}

@@

%Add me: \cite{Kirby13}

@@

\section{Introduction}
% POINT: LIGO soon will detect compact binary mergers....
%     ... and possibly EM counter part too
%     ... which will enable new physics
Gravitational waves have been detected from  coalescing  black hole binaries \citep{DiscoveryPaper,LIGO-O1-BBH}. 
Over the next few years, ground-based gravitational wave detectors like LIGO 
and Virgo  should detect the gravitational
wave signal from many more similar merging compact binaries \citep{LIGO-O1-BBH,RatesPaper,gwastro-EventPopsynPaper-2016}, as well as  binary  neutron stars and black hole-neutron star binaries \citep{LIGO-Inspiral-Rates,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
%
The host galaxies of gravitational wave sources will be identified, either directly or statistically.  
On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
% People we can't afford the space to cite, alas:
%    - 2015arXiv150101986H   -
%    - 2013MNRAS.430.2121P - Rosswog recent
%    - Shibata group/Koutarou
In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
the sky position and therefore approximate birthplace of each merging binary.    
%
On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \citep{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
networks increase in number and sensitivity, these localizations will allow statistical and, eventually, unique identification of
host galaxies directly, even without associated electromagnetic emission.
%
As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
formation; see, for comparison,  \citet{2011MNRAS.412.1508M}, \citet{long-grb-GuettaPiran2007},
\citet{2014ARAA..52...43B}, and references therein. %2010ApJ...722.1879M,2010MNRAS.407.1314M}.     
%

@@

%{\bf Richard go ahead and edit this however is needed.}  
The evolution
of a galaxy, in terms of its stellar mass and metallicity evolution,
depends strongly on its interaction history.  Galaxies which appear
similar at the present day may have had drastically different
histories, which may result in differences in compact object merger
rates.  To investigate whether galaxy history affects the compact binary event
rate, we have chosen two simulations which are extremely similar at $z
= 0$ but differ strongly in their merger histories; see Figure \ref{fig:images}.

@@

  Due to the differences in merger histories, the star formation histories and metallicity
  evolution of h258 and h277 also differ at early times.  Figure
  \ref{fig:TwoGalaxies} shows the star formation history (left panel) and metallicity evolution (right panel) of the two galaxies.  The star formation histories are quite different at early times, where h277 has larger bursts of star formation between 2-4 Gyr, but h258 has a large burst at $\sim 6$ Gyr during a major merger.   The right panel shows the mean metallicity of
  recently formed stars vs time (thick solid lines), where we define
  recent as within the past 50 Myr.  The shaded regions correspond to
  one standard deviation of the mean, while the thick dashed lines
  represent the top and bottom 90\%.  We see that the early evolution
  of the metal properties of these galaxies does differ - between 0.5
  and 6 Gyr, h277 hosts a \emph{modestly}  more metal-rich population than
  h258.   For most astrophysical processes, the small metallicity difference illustrated here will have no impact on
  present-day observables.  However,  the population of binary black holes  depends sensitively on all low metallicity star formation
  over cosmic time; as we show below, these small differences can have an observable impact at present.

@@

Our goal in this work is to estimate the \emph{ratio} of compact binaries that should be merging, at present, in the two
simulated Milky-Way analog galaxies described above.

To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \abbrvPSgrb{} (\cite{PSgrbs-popsyn}) and \abbrvPSellipticals{} (\cite{PSellipticals});  similar approaches have been used by
\cite{2016arXiv160508783L} and others.

@@

\begin{widetext}
% POINT:  Model
To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
\begin{eqnarray}
V = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 dm_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
\end{eqnarray}
where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  For neutron
stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
highly simplified model: the black hole masses are uniformly  drawn from $5 M_\odot$ to the maximum 
black hole mass $M_{max}(Z)$ allowed by
\emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
  therein]{gwastro-EventPopsynPaper-2016}.  In agreement with much more detailed prior work \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, this simplified model yields typical chirp masses for BH-NS binaries that
vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
$4.3 M_\odot$ in low-metallicity environments.  Not least because the average chirp mass for BH-NS simply cannot vary
dramatically, given the functional form of $\mc$, our results do not depend sensitively on the choice of black hole mass
distribution.  Finally, for binary black holes, we assume  comparable-mass binaries
form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
 between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise, adopting a fiducial exponent $p=2$; see, e.g.,
\cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
detection-weighted mass distribution [$\propto p(m_1,m_2)
\mc^{15/6}$] depends weakly on mass [$ p(m_1,m_2)
\mc^{15/6} \propto m_1^{-0.5} \delta(m_1-m_2)$.  In our simple model, the total  and chirp mass
distributions   are qualitatively consistent with detailed  binary evolution calculations \citep{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.

@@

To characterize how often compact binaries form and coalesce, we use the ansatz adopted in \abbrvPSellipticals{} and
\abbrvPSgrb{}: for a star-forming parcel of mass $\Delta M$ the number of binaries born at time $0$ which
are coalescing now is $\lambda \Delta M dP/dt$, where $\lambda$ is an overall efficiency per unit mass and $P(<t|Z)$ is
a metallicity-dependent delay time distribution.\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
    In this paper we are investigating the relative contribution of
different star-forming environments and galaxy evolutionary histories, not the overall normalization, so the overall scale of $\lambda$ is irrelevant.  
However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact
objects, we adopt a power law
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{min}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adopt a  concrete scale
factor  $\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{},
\abbrvPSellipticals, and \abbrvKBLowZa).
% DOCUMENTATION FOR CHOICE
%    - classic figures on event rate vs metallicity from Dominik #1.5  (see WVU talk slide 16)
%        2012-11-WVU/2012-11-WVU-Keynote.key 
%      Based on event rate changing by x10^4 over 1 order of magnitude. This includes both mass factor and
%      intrinsic factor.  Mass factor changes by x10, so intrinsic factor is x10^3 over x10 in Z, so a=3 is better.
%    - saturation will occur after a factor of 10^4
%    - Can also calibrate to change in event rate from Z sun to 0.1Zsun (i.e., a factor of 10 for model B)
%      a=1.  This is MUCH BETTER DOCUMENTED and MORE CONSERVATIVE.
To calibrate the exponent, based on Tables 2 and 3 of
\cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} (model B), for binary black holes and black hole-neutron star
binaries, we adopt $a=1$, while for binary neutron stars we adopt $a=0$; see, e.g., their Table 1 and Figures
5-7.\footnote{This choice of exponent provides an extremely conservative assessment of the impact of low Z
\cite[see,e.g.][]{2012CQGra..29n5011O,gwastro-EventPopsynPaper-2016}. } 
For binaries containing neutron stars, for simplicity and without loss of generality we adopt the universal delay time distribution
%% Finally, we parameterize the delay time distribution by  either
%% \begin{eqnarray}
%% P_t(<t) &=& \begin{cases}
%% 0 & t<10 \unit{Myr} \\
%% (t/13\unit{Gyr})^{b}& t \in [10\unit{Myr},t_H]
%% \end{cases} 
%% \end{eqnarray}
%% with $b> 0$ or as the special case
\begin{eqnarray}
\frac{dP_t(<t)}{dt} =  \begin{cases}
0 & t<10 \unit{Myr} \\
\frac{1}{t \ln (13 \unit{Gyr}/10\unit{Myr})} & t \in [10\unit{Myr},13\unit{Gyr}]
\end{cases} 
\end{eqnarray}
\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
  These variations have less impact on our results than the evolving metallicity distribution of star forming gas.}
For binary black holes forming at metallicities $Z<0.25 Z_\odot$, we adopt the same prescription.  
For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
  an extreme example of this well-known trend.] 
To be qualitatively consistent with detailed binary evolution calculations at near-solar metallicity (e.g., \abbrvPSellipticals{} and
\cite{gwastro-EventPopsynPaper-2016}), for 
black holes forming at metallicities $Z>0.25 Z_\odot$ we adopt a much more uniform delay time distribution, so 
coalescing black hole binaries have nearly uniform delay time distribution between $100\unit{Myr}$ and
$13\unit{Gyr}$\editremark{checkme again - a little hacky}; that said,  our conclusions are not sensitive to this choice.
For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
evolution  \citep{2010ApJ...715L.138B,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2-StarTrackRevised-2012}.

% POINT: Net effect
Therefore, up to an irrelevant overall scale factor, the  present-day detection-weighted coalescence rate $r_D$  of binary compact objects formed by within two similar
galaxies  can be calculated via
\begin{eqnarray}
 r_D \propto  \int d\log Z  \int _{13 \unit{Gyr}}^0dt  V(Z) \lambda(Z) \frac{dP_t}{dt}(t) \dot{M} p(\log Z|t)
\end{eqnarray}

@@

\begin{table}
\begin{centering}
\begin{tabular}{|ll|l|}\hline
 \text{\BoringGalaxy} & \text{BHBH} & 0.012 \\
 \text{\ExcitingGalaxy} & \text{BHBH} & 0.0116 \\
 \text{\DwarfOne} & \text{BHBH} & 0.0207 \\
 \text{\DwarfTwo} & \text{BHBH} & 0.0524 \\
 \text{\BoringGalaxy} & \text{BHNS} & 0.000219 \\
 \text{\ExcitingGalaxy} & \text{BHNS} & 0.000264 \\
 \text{\DwarfOne} & \text{BHNS} & 0.000275 \\
 \text{\DwarfTwo} & \text{BHNS} & 0.000235 \\
 \text{\BoringGalaxy} & \text{NSNS} & 0.000206 \\
 \text{\ExcitingGalaxy} & \text{NSNS} & 0.000228 \\\hline
\end{tabular}
\end{centering}
\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
  discussed.  
}
\end{table}
